\subsection*{Dysnolar}
\index{Gods!Dysnolar}
\begin{goddesc}
\Level{Major}
\Domains{War}
\Symbol{A rusted-out helmet}
\end{goddesc}
Dysnolar is the god of fighting relentlessly.
Embodying the unending stamina some soldiers seem to have for killing, he is a terrifying monstrosity with very few clerics.

\subsubsection*{Personality}
Dysnolar seems to have no ability to speak, or to think.
All he does is fight, manifesting on the battlefield during the most intense battles.
There is no recorded history of him speaking, although some witnesses have reported that he has said the single word "why" in a wet, raspy voice, like that of a man with a punctured lung.

\subsubsection*{Physical Appearance}
According to legend, Dysnolar was once a handsome warlord god, well-known for his good looks and charm, even as he was committing terrible acts.
All traces of this form, if it ever existed, are now completely gone, supposedly the result of a fight with Tecumtaz that Dysnolar ultimately lost.

Dysnolar currently appears as a huge suit of armor, thirty feet tall or more.
The armor is rusted and covered in blood stains, and it wields a shattered longsword.
Inside the armor there is nothing but black smoke, which swirls and twists rapidly as if inside a tornado.
Some say that this smoke is actually made of the souls of his clerics, who join their horrible patron after their deaths.

\subsubsection*{World Temple Room}
The appearance of Dysnolar's world temple room is unknown.
Nobody has ever entered and left alive.
From the doorway, all that can be seen is a black void, with the faint sounds of screaming coming from within.