

Magic in Spirals, on the surface, is similar to magic in other worlds.
Mechanically it works much the same: it may be granted in a variety of ways, channeled into spells, and brewed into potions.
Beneath the surface, however, the way the world of Spirals interacts with its magic is quite different.

\begin{multicols}{2}
\subsection{Presence}
In Spirals, the presence of magic is felt in the lives of all creatures.
It is what holds the Tendrils together, gives them form and substance, lights them during the day, and, occasionally, creates them from nowhere.

\subsection{Arcane Magic}
When an arcane caster uses a spell in Spirals, they seek to move the ambient magic around them, to give it form and substance.
This is a dangerous task indeed---magic, at its core, \textit{desires} to be used, to make its mark on the world, and it eagerly rushes to a caster, attempting to make that desire reality.
Unfortunately for the caster, however, the eagerness of the magic to be used does not extend to a desire to be controlled, or to be limited.
Without careful focus and application of arcane techniques, the caster will lose control of her magic, and it will run wild within her.
This can have a wide variety of effects, but, unfortunately, the most common by far is to cause the caster to burst into flames.

\subsubsection{Enchanting}
Spirals has a lot of ambient magic, and clever wizards can tap into it, creating enchanted objects.
For simple enchantments this is not difficult.
If one wishes, for example, they could easily direct ambient magic to propel a vehicle or heat a bit of metal.
These simple energy transfer spells are reliable, and, as a result, vehicles like landcycles and magical forges are somewhat common.

Spells which require higher levels of precision, however, are much harder to contain within an object.
If one wished to create a sword which cut through enemies more efficiently, for example, they would need to take care to temper the enchantment so it draws only the required amount of energy from the surrounding area.
Failure, of course, would result in the sword exploding violently the moment the enchantment was cast.
As a result, enchanted weapons and items are rarer than in other settings, as they are more difficult to make.
It should be noted, however, that the high levels of ambient magic increases the overall potential for enchanted items.
Few, if any, wizards have ever lived who were skilled enough to take advantage of this potential, but, if they could, the results could be wondrous (or devastating) indeed.

\subsection{Magic Derived from Nature}
Those who walk in wild places may have magic of their own.
Unlike arcane magic, it is not derived from the listless sort of magic that simply exists, but from a more purposeful, directed form: that which gives nature its shape.
This magic is found in the ground of the Tendrils, and in the features on (or below) their surface.
It is more introspective, gentler than the arcane magic, granting wondrous abilities to those it deems worthy. 

\subsubsection{Magical Creatures}
The greater presence of magic results in a greater presence of magical creatures, as well.
Dragons in Spirals are still relatively rare, for example, but there are still enough of them that almost all the larger armies are able to contract a few for special operations work.
Horrifying monsters such as mind flayers or beholders, too, are in no short supply.
Giant animals, too, are fairly commonplace.

This seems like it may be cataclysmically disastrous for mortal civilization, but, in truth, it's not as bad as you'd think.
The magic that allows the world to be filled with wyverns and Slaads also brings up powerful heroes who can deal with such things.

\subsubsection{Nature without Life}
Unlike in other settings, the magic of nature is not necessarily the magic of life---Tendrils covered in parched desert or suffocating ice have magic in equal measure as those painted with plants and trodden upon by animals.
This magic, however, rarely allows itself to be used by those among the living, preferring the inanimate.
When it does allow itself to be used, it is generally out of self-preservation: the desire to have its domain kept as it likes it, with little life.
These servants rarely cause direct harm to the living, as the rotting of flesh is itself a haven for life, choosing instead to expel the living to more suitable places.
\label{druidofdecay}
Occasionally, however, a desolate place will grow discomforted, unsatisfied with its domain.
In these cases, a Druid of Decay may arise, blindly serving his or her arcane master, singly devoted to the goal of expanding desolation and removing life.
Most often these evils are quickly dispatched by those who preserve living nature, but they occasionally may have a larger effect.

\begin{adventureidea}{Desolation}
Druids of decay, when they arise, are a horrible plague upon the world.
They are often extremely powerful, and hell-bent on expanding the desolation of their home tendril into other, vibrant areas of life.
Worse, they often retain their sanity and ability to plan, making them dangerous foes.

A druid of decay can make a great antagonist for your campaign, especially because they can have such variance in personality.
Some are actually quite diplomatic: they'll give the populations of towns and cities a chance to retreat before destroying them, and might even intentionally scare off animals as they spread their desolation.
Others are significantly less charitable, and may intentionally cause as much death as they possibly can.
\end{adventureidea}

\subsection{Magic Divine}
Divine magic, as the name implies, stems from the Gods.
The divine power of the gods may be sent across great distances, loaned to their servants so they may perform great works.
The gods also use this magic directly when dealing with mortal affairs, although they only intervene in such a manner when absolutely necessary.

Divine magic is by far the safest type of magic.
Being completely regulated by a caster's patron, there is no risk that it will overcome the caster or spin wildly out of control.
Unfortunately, this safety comes with a caveat of lifestyle---one must serve a god or goddess in order to use it, and they near-universally require strict lives of service and works from their clerics.

Divine magic can also sometimes be used by those with extreme purity of will,\footnote{Note that, in this context, "pure" does not mean "holy" or "righteous", but "untainted." If one has an extreme and concentrated desire to commit horrible acts, they too can use such magic---often to horrifying ends.} such as paladins who have not sworn allegiance to any particular god.
This magic is equally safe as god-derived magic, but only as long as the user's will remains pure and focused on their task.

The nature of divine magic and arcane magic, on a fundamental level, seems remarkably similar.
Various energy tests performed at wizarding colleges have confirmed that the two varieties share almost all of their fundamental properties.
This has led some wizards to believe that gods are merely extremely magical beings.
Some have even attempted to ascend to godhood themselves via the use of ancient artifacts or complex rituals, a task which almost always results in nothing more than an extremely large explosion.
\end{multicols}
 
 
 \input{chapters/structure/rwm}

