\subsection*{Bahamut}
\begin{goddesc}
\Level{Major}
\Domains{Knowledge}
\Symbol{The head of a dragon, in silver}
\index{Gods!Bahamut}
\end{goddesc}
\begin{itquote}
Yes, it is true that we dragons can survive more easily than what some would call the ``lesser'' races, but we are called to things much greater than survival.
Our power, then, does not serve to make our lives easier, but provides a joyous burden, a responsibility to the truth and justice that few have the honor of bearing. 
\end{itquote}
\QuoteAttr{Teachings of the Silver Dragon Syralth}
Bahamut, the lord of good dragons, is a powerful force for good in the world of Spirals.
An ancient and powerful God, he has been alive for as long as mortals have recorded history, and still interacts with the world on a daily basis.
Unlike his Sister, he believes that those in power must use that power to help those weaker than them.
This includes power gained by virtue of being a giant, dangerous monster, but also power gained via wealth or political ability.
\subsubsection*{Personality}
Bahamut is a kind soul with a firm personality.
It is rare to see a smile grace his features, and he can be stern in his dealing with his clerics.
He is calm and restrained, for the most part, but is somewhat prone to terrible fury when provoked.

In certain forms, the dragon's personality may be altered.
When traveling in the disguise of an old man, for example, he can seem almost mad, laughing for no discernible reason and sprouting vague prophecies.
Popular belief is split on why he does this.
Many assume it is simply a form of stress relief, or a calculated act to help him reach certain goals.
Others, however, claim that the temporary insanity is legitimate, although explanations as to why vary greatly.

\subsubsection*{Physical Appearance}
Bahamut normally takes the form of a colossally large dragon, majestic and beautiful in the same way as a piece of great architecture.
His scales shimmer and glow as if light by moonlight, and his dark grey eyes seem to contain storms.

Bahamut occasionally travels in other forms as well.
Most notably, he often mingles among mortals in the form of a human, appearing as either an insane old man wearing tattered robes or a handsome noble in a simple cloak.

\subsubsection*{Responsibilities}
Bahamut is responsible for helping the powerful to be just in their dealings.
This includes his children, the good dragons, but also kings and powerful adventurers.

Clerics of Bahamut can be either mortal or draconic.
Often, mortal clerics will learn his teachings and rites from one of his more devout dragon followers, typically in one of several temples around the world.


Bahamut's clerics swear to keep the powerful in check, typically by acting as ethical advisors to rulers and business owners.
They are not afraid to resort to violence to remove one who abuses power, but tend to try other methods first, including sly economic maneuvers. 
Still, it is not unheard of for a tyrannical king to burn to death at the hands of a gold dragon. 

\subsubsection*{World Temple Room}
Bahamut's complex in the world temple is impressive, so much so that many clerics who do not worship the platinum dragon make stops to visit it when on official business for their own guards.
The marble walls are coated in artwork, and every room has at least one sculpture.
A grand red carpet leads to the throne room of the god himself, where he sits surrounded by yet more art, as well as a carefully-organized collection of history books.
A door behind his throne leads to the room where he keeps his own horde, which consists largely of enchanted weapons, along with coins and other treasure.

Bahamut's temple is not only inhabited by the god himself, but also his most trusted servants.
A variety of ancient clerics live in the temple, performing divine research, surveying the outside world, and occasionally even answering prayers on their master's behalf.
These clerics have their own rooms, as well as common working areas that they all share.

The vast majority of those invited to live with the god are dragons, but Bahamut will occasionally grace a member lesser race this honor if they perform great feats in his name.
For a cleric loyal to the platinum god, this is an honor unimaginable.

\subsection*{Byr'nke the Wise}
\index{Gods!Byr'nke}
\begin{goddesc}
\Level{Intermediate}
\Domains{Knowledge}
\Symbol{Three gold coins surrounding an eye}
\end{goddesc}

God of money and monetary policy, Byr'nke the wise is a respected, if little-known, deity.
Whenever wise and prudent treasurers discuss their currency, his presence is felt, guiding their gentle hands.

\subsubsection*{Personality}
Byr'nke is a kind, if somewhat distant, god.
His clerics help in just financial institutions the world over, guiding their decisions and easing their extreme stress.
Some even rumor that Byr'nke's avatar will occasionally instruction students on the subject of economics at several colleges throughout the world.

\subsubsection*{Responsibilities}
Byr'nke is responsible for conducting monetary policy on the common pieces of platinum, gold, silver, and copper, although kingdoms with their own specific currency control their own supply.
He conducts this policy with the goal of keeping the economy as stable as possible.
Byr'nke has the sole authority to issue new currency in pursuit.

Byr'nke's independence is integral to his ability to carry out his mission.
Many of the other gods care greatly about this independence, as they know that any breach of it would cause immediate financial disaster, and are often willing to fight to defend it.

Byr'nke's clerics are almost entirely presidents of banks, who operate throughout Spirals.
Once a year he meets with ten of them to discuss the economy, set interest rates, and decide on further actions to take.
These clerics almost never get into real fights, much less go on a grand adventure.

Those clerics who do not manage banks mostly handle counterfeiters, or try to stabilize the world in general to stabilize the economy.
These clerics are interesting to work with, taking a more technocratic, measured approach to their actions, rather than being filled with religious zeal.

\subsubsection*{Physical Appearance}
Byr'nke takes the form of a humanoid in banker's robes.
His exact species changes depending on the audience: elven when among elves, human amidst humans, and dwarven in the presence of dwares.
Some have even claimed that he has draconic or demonic forms, although they are rarely used if they exist.
The only common feature among his forms is his facial hair, a short goatee.

\subsubsection*{World Temple Room}
Byr'nke's room is extremely small.
it consists of several offices, occupied by his clerics, and one head office, occupied by himself.
There is also a boardroom where he meets with financial leaders or other gods.
The table in this room was donated to him as a gift from Bahamut, and is quite impressively made of solid gold.

\subsection*{Tecumtaz}
\index{Gods!Tecumtaz}
\begin{goddesc}
\Level{Major}
\Domains{War}
\Symbol{A flaming hammer}
\end{goddesc}
\begin{itquote}
Somehow, despite your age, you seem to be under the boyish impression that war is something which can bring glory and honor to your people.
I can assure you, it is nothing of the sort---but, in your foolishness, you decided upon this war, and my servants intend to give you what you have requested.
\end{itquote}
\QuoteAttr{Letter to the Warlord Alocoth}
Tecumtaz is the god of just war, and perhaps one of the strangest gods in Spirals.
Wherever mortal fight tyranny and oppression, he is there, but he is not a god of kindness, and is barely one of restraint.

\subsubsection*{Personality}
Tecumtaz hates war.
This simple fact burns throughout his personality and actions.
Unlike other deities of war, who respect great warriors and bless mighty conquerors, the mightiest soldier in Tecumtaz's eyes is the one who ends the conflict the most quickly and justly, honor be dammed.
This hatred seeps into all other parts of his personality.
The face he presents to those who righteously end conflicts is one of supreme kindness, almost familial in nature.
To those fools who start senseless conflict, however, Tecumtaz presents a very different face, one full of terror and fury beyond all mortal comprehension.
This includes many other gods, even ones who supposedly share his alignment and domain.

\subsubsection*{Responsibilities}
Tecumtaz takes it upon himself to prevent wars from happening, and to stop them as quickly as possible when they do arise.
Tecumtaz does not permit his clerics to perform evil actions, such as murdering the innocent, but he doesn't really care about honor.
If a cleric of Tecumtaz is to join a war, one can expect absolute chaos---scorched-earth tactics, destruction of civilian property, assassinations of generals, and large-scale mayhem, although they will firmly prevent the deaths of the innocent.
One will also expect that, for better or for worse, the war will soon be over.

\subsubsection*{Physical Appearance} 
Tecumtaz most often takes the form of a man in an officer's uniform.
When enraged, his eyes glow with terrible fire.

\subsubsection*{World Temple Room}
Tecumtaz's room in the world temple takes the form of a military encampment at dusk, a vast field filled with several tents.
The air inside is cool and damp.
Tecumtaz himself takes position within the officer's tent, which is only slightly bigger than the rest.
Any clerics who happen to be residing with him stay in other tents.
