\subsection*{Tiamat}
\index{Gods!Tiamat}
\begin{goddesc}
\Level{Major}
\Domains{Knowledge}
\Symbol{Five Dragon Heads in Profile}
\end{goddesc}

Tiamat is the dragon goddess of greed and wealth, as well as the mother of all dragons.
You most likely recognize her---she's present in many D\&D settings, although her personality in Spirals is  altered.
Tiamat, like Bahamut, is an extremely old God, and has spent most of her long life gaining power in any way she can.

\subsubsection*{Personality}
Tiamat is a pragmatic deity, perhaps more so than any other draconic deity, or even most dragons.
Although she does maintain a magnificent horde, she views it over the long-term, and is perfectly willing to part with large parts of it if she may profit later.
It is not uncommon for her to loan her clerics rare magical items, scrolls, or other useful items.
She has even been known to give those exceptionally loyal to her small gifts, to incentivize similar behavior in others.
She is more than willing to forge deals with other gods, or even powerful mortals, and is a surprisingly reliable partner---although her help will tend to cost you dearly.

Over the millennia, it has become impossible to determine exactly how much influence Tiamat has.
It is rumored that almost every major noble family owes her some sort of favor, that she has a direct hand in the day-to-day operations of major criminal groups, and that even other gods are in her debt.
\subsubsection*{Physical appearance}
Tiamat typically takes the form of a dragon with five heads, one for each chromatic color.
She occasionally also takes the form of a beautiful young woman, dressed in stupendously valuable clothing.
Both forms retain the dangerous glint in her eyes.

\subsubsection*{Responsibilities}
Tiamat acts with the goal to maximize her own power and wealth in the long-term, even though she is technically supposed to guide all who are ambitious.
She views her children, the chromatic dragons, as an extension of herself, and is willing to pull some strings to allow them to obtain power, as well.

All of Tiamat's clerics have sworn a magically-enforced allegiance to her.
In exchange for their undying loyalty, Tiamat will often let them obtain large amounts of wealth, and even control of a kingdom or two.
Her mortal clerics act in underhanded, clandestine ways to enact the will of the Dragon Queen more often then they participate in obvious violence, and she employs a large number of assassins.

\subsubsection*{World Temple Room}
Tiamat's room in the world temple takes the form of an elegant palace.
The walls are lined with platinum, carved into intricate murals, and decorated with fine art.

Behind her throne, in a room only she may access, Tiamat keeps the bulk of her horde.
Few have set eyes on it, and fewer have spoken of it afterwards.
What can be said for certain is that it is staggeringly large, and contains items the likes of which can hardly be described.

\subsection*{Bane}
\index{Gods!Bane}
\begin{goddesc}
\Level{Major}
\Domains{Trickery}
\Symbol{A cloud of smoke}
\end{goddesc}
Bane, the god of fear and tyranny, is one of the most hated (and most worshipped) gods in the Spirals pantheon.

\subsubsection*{Personality}
Bane's personality is surprisingly charismatic.
He is confident, oddly funny, and even cordial.
Even those who hate what he stands for must admit that he is quite the charmer.
Tyranny, of course, is best executed by a leader who is at least somewhat liked, and fear is most effective when one's guard is down.

\subsubsection*{Physical Appearance}
Bane normally takes the shape of a handsome man, in his mid-twenties, wearing a black robe.
When he wishes to personally spread fear, he takes on an amorphous form, like black smoke.
This form quickly morphs to depict what the viewer fears most.
When in this form, all that view him must succeed on a DC 30 wisdom saving throw, or become frightened for 1d8 days.

\subsubsection*{World Temple Room}
Bane's world temple complex is extremely sparse.
It consists mainly of his throne and a few portraits of himself.
All else is located behind a small door, which has his symbol on it.
Many have been brought behind the door---none returned in any state to tell the outside world what they saw.